---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: Bennie Yang
    url: https://example.com/norajones
    affiliation: SMU MITBs
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# The Task

Using either calendar heatmap or horizon graph, prepare a data visualisation showing the historical stock prices between 1st January 2020 - 31st December 2021 by the top 40 companies by market capitalisation. 

# 1.0 Challenges

1. Data has to be scraped from Yahoo! Finance

2. Large number of companies to be represented in visualisation


# 2.0 Sketch of Visualisation

# 3.0 Step-by-step Preparation

## 3.1 Install and load required libraries

```{r, echo=TRUE}
packages = c('rvest', 'tidyverse', 'tidyquant', 'janitor')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
    }
  library(p,character.only = T)
}
```

## 3.2 Scrape data from Yahoo! Finance

Define variables for start and end dates

```{r, echo=TRUE}
from_date <- "2020-01-01"
to_date <- "2021-12-31"  
period_type = "days" 

stock_data_daily = tq_get("SE",
               get = "stock.prices",
               from = from_date,
               to = to_date) %>%tq_transmute(select     = NULL, 
               mutate_fun = to.period, 
               period  = period_type)
  
```

Define list of tickers for top 40 companies by market capitalisation
```{r, echo=TRUE}
top40 <- c("SE","DBSDF","O39.SI","U11.SI","SNGNF","WLMIF","GRAB","")  

stock_data_daily = tq_get(stock_selected,
               get = "stock.prices",
               from = from_date,
               to = to_date) %>%tq_transmute(select     = NULL, 
               mutate_fun = to.period, 
               period  = period_type)

  
```

# 4.0 Discussion




