---
title: "In-Class Exercise 5"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=TRUE}

packages = c('corrplot', 'tidyverse', 'ggstatsplot','corrgram','ellipse','ggcorrplot')

for(p in packages){library
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

```{r}
wine <- read_csv("data/wine_quality.csv")
```

```{r, fig.width=7, fig.height=7}
pairs(wine[,2:12])

```

Don't show upper panel using upper.panel argument
```{r, echo=TRUE, , fig.width=7, fig.height=7}
pairs(wine[,2:12], upper.panel = NULL)
```

Don't show upper panel using lower.panel argument
```{r, echo=TRUE, fig.width=7, fig.height=7}
pairs(wine[,2:12], lower.panel = NULL)
```


Show correlation coefficients
```{r, fig.width=7, fig.height=7}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...) {
usr <- par("usr")
on.exit(par(usr))
par(usr = c(0, 1, 0, 1))
r <- abs(cor(x, y, use="complete.obs"))
txt <- format(c(r, 0.123456789), digits=digits)[1]
txt <- paste(prefix, txt, sep="")
if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
text(0.5, 0.5, txt, cex = cex.cor * (1 + r) / 2)
}

pairs(wine[,2:12], 
      upper.panel = panel.cor)
```
Note: X in correlogram mean not statistically significant
```{r, fig.width=7, fig.height=7}


ggstatsplot::ggcorrmat(
  data = wine, 
  cor.vars = 1:11,
  ggcorrplot.args = list(outline.color = "black", 
                         hc.order = TRUE,
                         tl.cex = 10),
  title    = "Correlogram for wine dataset",
  subtitle = "Four pairs are no significant at p < 0.05",
  type = "p")
  

ggplot.component = list(
    theme(text=element_text(size=3),
      axis.text.x = element_text(size = 5),
      axis.text.y = element_text(size = 5)))

```

```{r}


ggplot.component = list(
    theme(text=element_text(size=5),
      axis.text.x = element_text(size = 8),
      axis.text.y = element_text(size = 8)))

```

Build multiple plots 
```{r, fig.width=14, fig.height=7}


grouped_ggcorrmat(
  data = wine,
  cor.vars = 1:11,
  grouping.var = type, #to specify basis to split data for diff plots
  type = "robust",
  p.adjust.method = "holm",
  plotgrid.args = list(ncol = 2), #to specify number of columns in overall image
  ggcorrplot.args = list(outline.color = "black", 
                         hc.order = TRUE,
                         tl.cex = 10),
  annotation.args = list(
    tag_levels = "a", #numbering of subsplots "a" for small letters, "I" for Roman, "1" for numbers
    title = "Correlogram for wine dataset", #Overall title
    subtitle = "The measures are: alcohol, sulphates, fixed acidity, citric acid, chlorides, residual sugar, density, free sulfur dioxide and volatile acidity", # overall subtitle
    caption = "Dataset: UCI Machine Learning Repository"
  )
)

```

Using corrplot for clustering.
Generate correlation matrix
```{r, fig.width=14, fig.height=7}
wine.cor <- cor(wine[, 2:11])
```

Plot the corrplot. Default visual is circles
```{r, fig.width=7, fig.height=7}
corrplot(wine.cor)
```
Apply clustering using arguments order, hclust.method. Display rectangle to group clusters using addrect.
```{r, fig.width=7, fig.height=7}
corrplot(wine.cor, 
               tl.pos = "lt",
               tl.col = "black",
               order="hclust",
               hclust.method="ward.D",
               addrect =3)
```
Plot the corrplot. Default visual is circles. specify visual using method argument.
```{r, fig.width=7, fig.height=7}
corrplot(wine.cor, 
         method = "ellipse", 
         type="lower",
         diag = FALSE,
         tl.col = "black")
```
Plot mixed plot using corrplot.mixed()
```{r, fig.width=7, fig.height=7}
corrplot.mixed(wine.cor, 
               lower = "ellipse", 
               upper = "number",
               tl.pos = "lt",
               diag = "l",
               tl.col = "black",
               order="hclust",
               hclust.method="ward.D",
               addrect =3)
```
